Incentivizing Exploration with Unbiased History

### 2018-11-02 llevel-overview.tex
editing...

A natural idea to extend the three-level policy is to insert more
levels as multiple ``check points", so the policy can incentivize the
agents to perform more adaptive exploration. However, we need to
introduce two main modifications in the info-graph two accomendate
some new challenges. We will first informally describe our techniques
the two-arm case.

@@

We will leverage the following key observation: in order to maintain
the ``lucky'' property, it suffices to have agents in different $l$-th
level groups to observe disjoint sub-histories that takes place in
level $(l - 1)$. Moreover, as long as the group size in levels lower
than $(l-1)$ are substantially smaller than group size of level $l-1$,
the ``lucky'' property does not break even if different groups in
level $l$ observe overlapping sub-history from levels
$\{1, \ldots, l-2\}$.

>>>>

A natural idea to extend the three-level policy is to insert more
levels as multiple ``check points", so the policy can incentivize the
agents to perform more adaptive exploration. However, we need to
introduce two main modifications in the info-graph two accomendate
some new challenges. We will first informally describe our techniques
for the two-arm case.

@@

We will leverage the following key observation: in order to maintain
the ``lucky'' property, it suffices to have the agents in different
$l$-th level groups to observe disjoint sub-histories that takes place
in level $(l - 1)$. Moreover, as long as the group size in levels
lower than $(l-1)$ are substantially smaller than group size of level
$l-1$, the ``lucky'' property does not break even if different groups
in level $l$ observe overlapping sub-history from levels
$\{1, \ldots, l-2\}$.
